% ============================================================================
%  SOFTWARE ENGINEERING CV — SAMIR GUENCHI (One Page)
% ============================================================================
\documentclass[8pt, letterpaper]{extarticle}

% ---------- CORE PACKAGES ----------
\usepackage[left=0.3in, right=0.3in, top=0.25in, bottom=0.25in]{geometry}
\usepackage{multicol}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{fontawesome5}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{xcolor}
\usepackage{microtype}
\usepackage{ragged2e}

% ---------- COLOUR PALETTE ----------
\definecolor{accent}{HTML}{1A3A5C}
\definecolor{linkblue}{HTML}{2563EB}
\definecolor{rulecolor}{HTML}{3B6FA0}

% ---------- HYPERLINK STYLE ----------
\hypersetup{
    colorlinks=true,
    linkcolor=accent,
    filecolor=accent,
    urlcolor=linkblue,
    pdfauthor={Samir Guenchi},
    pdftitle={Software Engineering CV — Samir Guenchi},
}

% ---------- SECTION FORMATTING ----------
\titleformat{\section}
  {\color{accent}\large\bfseries\scshape}
  {}{0em}{}
  [\vspace{-4pt}{\color{rulecolor}\rule{\linewidth}{0.8pt}}]
\titlespacing{\section}{0pt}{6pt}{3pt}

% ---------- GLOBAL SPACING ----------
\setlength{\columnsep}{0.25in}
\setlength{\parindent}{0pt}
\setlist{nosep, leftmargin=1em}
\pagestyle{empty}

% ========================================================================
\begin{document}

% ========================= HEADER =========================
\begin{center}
    {\fontsize{20}{24}\selectfont\bfseries\color{accent} SAMIR GUENCHI} \\[4pt]
    {\small
      \faIcon{envelope}\;\href{mailto:samir.guenchi@ensia.edu.dz}{samir.guenchi@ensia.edu.dz}
      \quad\textcolor{rulecolor}{$\boldsymbol{\cdot}$}\quad
      \faIcon{phone-alt}\;+213 780066761
      \quad\textcolor{rulecolor}{$\boldsymbol{\cdot}$}\quad
      \faIcon{map-marker-alt}\;Algiers, Algeria
    }\\[2pt]
    {\small
      \faIcon{linkedin}\;\href{https://linkedin.com/in/guenchi-samir}{linkedin.com/in/guenchi-samir}
      \quad\textcolor{rulecolor}{$\boldsymbol{\cdot}$}\quad
      \faIcon{github}\;\href{https://github.com/Samir-Guenchi}{github.com/Samir-Guenchi}
      \quad\textcolor{rulecolor}{$\boldsymbol{\cdot}$}\quad
      \faIcon{code}\;\href{https://codeforces.com/profile/Guenchi_Samir_ia}{codeforces.com/profile/Guenchi\_Samir\_ia}
    }
\end{center}
\vspace{2pt}

% ======================== TWO COLUMN LAYOUT ============================
\begin{multicols}{2}
\RaggedRight

% -------------------- SUMMARY --------------------
\section*{{\color{accent}\faIcon{user-tie}}\; Professional Summary}
Final-year AI \& Data Science Engineering student at ENSIA with hands-on experience building full-stack web applications, scalable REST APIs, real-time systems, and enterprise data pipelines. Proficient in React, Node.js, TypeScript, Python, and PostgreSQL. Delivered multiple production e-commerce platforms end-to-end as a freelance engineer and contributed to data infrastructure at Djezzy. Seeking a software engineering role to build impactful products at scale.

% -------------------- EDUCATION --------------------
\section*{{\color{accent}\faIcon{graduation-cap}}\; Education}
\textbf{Engineering Degree — Artificial Intelligence and Data Science} \\
National Higher School of Artificial Intelligence (ENSIA), Algeria \\
\textit{2021 – 2027 (expected)} — Cycle Préparatoire (2021–2024) + Cycle Supérieur (2023–2027) \\
Currently completing Final Year Project

% -------------------- EXPERIENCE --------------------
\section*{{\color{accent}\faIcon{briefcase}}\; Work Experience}

\textbf{Data Scientist Intern — Djezzy (DSIP Program)} \textcolor{rulecolor}{$|$} \textit{2026–Present} \\
\textbf{Project:} Built a natural language-to-SQL BI agent enabling business experts to query revenue and subscriber analytics without writing SQL. \\
\textbf{Stack:} LLM-based query translation, Kafka event-driven pipelines, SQL generation/execution, agentic result interpretation. \\
\textbf{Outcome:} Delivered a self-serve analytics pipeline on a horizontally scalable architecture, reducing dependency on manual analyst intervention. \vspace{3pt}

\textbf{Freelance Full-Stack Engineer — El Basma Boutique} \textcolor{rulecolor}{$|$} \textit{2025} \\
\textbf{Project:} Designed a production backend and multilingual e-commerce storefront for a traditional Algerian fashion brand, with integrated analytics, real-time communication, and business management APIs. \\
\textbf{Stack:} Node.js, Express, SQLite/Turso, JWT, RBAC, Socket.IO, webhook integrations (Meta, WhatsApp, TikTok), React 18, Vite, i18next, Framer Motion, Meta Pixel. \\
\textbf{Outcome:} Delivered a centralized backend with multilingual storefront (Arabic, Darija, French, English) and admin dashboard. \\
{\small \faIcon{github}\;\href{https://github.com/Samir-Guenchi/el-basma-backend}{Backend} \;\textcolor{rulecolor}{$\cdot$}\; \href{https://github.com/Samir-Guenchi/el-basma-website-front-end}{Frontend} \;\textcolor{rulecolor}{$\cdot$}\; \faIcon{external-link-alt}\;\href{https://el-basma-website-front-end.vercel.app/}{Live Demo}} \vspace{3pt}

\textbf{Freelance Full-Stack Engineer — Dahaoui Boutique} \textcolor{rulecolor}{$|$} \textit{2025} \\
\textbf{Project:} Built a complete e-commerce platform with customer storefront, inventory management, order processing, analytics, and administrative dashboard. \\
\textbf{Stack:} React, Node.js, Express, MongoDB, Cloudinary, Tailwind CSS, REST APIs, i18next. \\
\textbf{Outcome:} Delivered a feature-rich platform supporting multilingual shopping, inventory/order management, and business analytics. \\
{\small \faIcon{github}\;\href{https://github.com/Samir-Guenchi/dahaoui_boutique}{Repo} \;\textcolor{rulecolor}{$\cdot$}\; \faIcon{external-link-alt}\;\href{https://dahaoui-boutiquee.vercel.app/}{Live Demo}} \vspace{3pt}

\textbf{Software Engineer Intern — Algérie Poste} \textcolor{rulecolor}{$|$} \textit{Dec 2025 – Feb 2026} \\
\textbf{Project:} Built a multi-vendor e-commerce platform with an NLP-based seller reputation system (sentiment analysis on reviews) and RBAC across buyer, seller, delivery, and admin roles. \\
\textbf{Stack:} Node.js, TypeScript, PostgreSQL, NLP sentiment analysis. \\
\textbf{Outcome:} Delivered a reputation scoring system grounded in review content analysis, across a role-partitioned production platform. \vspace{3pt}

\textbf{Web Development Intern — HR TECHNOLOGY} \textcolor{rulecolor}{$|$} \textit{Aug – Sep 2024} \\
\textbf{Project:} Developed responsive web applications and enhanced user interfaces and website performance for production web projects. \\
\textbf{Stack:} React, JavaScript, HTML, CSS, responsive design, performance optimization. \\
\textbf{Outcome:} Delivered responsive, user-friendly web interfaces with improved application performance.

% -------------------- SKILLS --------------------
\section*{{\color{accent}\faIcon{cogs}}\; Technical Skills}
\textbf{Languages:} Python, JavaScript, TypeScript, HTML/CSS, SQL \\
\textbf{Frontend:} React 18, Vite, Framer Motion, Tailwind CSS, i18next \\
\textbf{Backend:} Node.js, Express.js, REST APIs, Socket.IO, JWT/RBAC \\
\textbf{Databases:} PostgreSQL, MongoDB, SQLite/Turso \\
\textbf{Infrastructure:} Kafka, Cloudinary, n8n, Git/GitHub, Vercel \\
\textbf{ML/AI:} PyTorch, NLP, Computer Vision, Deep Learning \\
\textbf{Cloud:} Oracle Cloud Infrastructure (certified) \vspace{3pt} \\
\textbf{Certifications:} Oracle Certified — Data Science \;\textcolor{rulecolor}{$\boldsymbol{\cdot}$}\; Oracle Certified — Cloud Infrastructure

% -------------------- LANGUAGES --------------------
\section*{{\color{accent}\faIcon{language}}\; Languages}
\textbf{Arabic} — Native \quad\textcolor{rulecolor}{$\boldsymbol{\cdot}$}\quad \textbf{French} — Fluent \quad\textcolor{rulecolor}{$\boldsymbol{\cdot}$}\quad \textbf{English} — Fluent

% -------------------- TEACHING --------------------
\section*{{\color{accent}\faIcon{chalkboard-teacher}}\; Teaching Experience}
\textbf{Competitive Programming Coach — Algerian Olympiad in Informatics (AOI)} \textcolor{rulecolor}{$|$} \textit{Apr – Oct 2025} \\
Designed and delivered algorithmic problem-solving lessons (A*, graph theory, optimization) to lycée students preparing for national and international olympiads. Helped prepare a student for IOI 2025.

% -------------------- EVENTS --------------------
\section*{{\color{accent}\faIcon{users}}\; Hackathons \& Events}
\begin{itemize}[leftmargin=*]
    \item \textbf{AAIET 2025} — International Conference on Applied AI, Djelfa (Dec 2025)
    \item \textbf{2023 Data Science Datathon} — Industry problems for Yassir \& Société Générale; predictive modeling under time constraints
    \item \textbf{ETCODE 2023} — Competitive programming hackathon (ENSIA Tech Community)
    \item \textbf{Mobile Ideathon (Mobai)} — Mobile app prototype for BMS; rapid prototyping and pitching
\end{itemize}

% -------------------- MEMBERSHIPS --------------------
\section*{{\color{accent}\faIcon{id-badge}}\; Professional Memberships}
\textbf{ENSIA Tech Community} — IT Department Member (2023) \\
\textbf{Club Scientifique EBEC (ENSIA)} — IT Manager (2024 – Sep 2025) — Led website development and technical infrastructure for events

\end{multicols}
\end{document}
